Effect of character correlation

### 2017-07-17 Analysis/EffectCorrelation.Rmd
Simplified vignette

Before starting
===============

Loading the functions
-----------------------------------

Getting the functions

```{r, eval = TRUE}
source("functions.R") ; load.functions(test = FALSE)
dyn.load("../Functions/char.diff.so")
load("../Data/NTS/matrix.nts.Rda")
```

Loading the data
-----------------------------------

Loading the tree comparisons from TreeCmp

```{r, message = FALSE}
## 25t_100c
bay_25t_100c <- read.TreeCmp("25t_100c", type = "Bayesian")
par_25t_100c <- read.TreeCmp("25t_100c", type = "Parsimony")

## 25t_350c
bay_25t_350c <- read.TreeCmp("25t_350c", type = "Bayesian")
par_25t_350c <- read.TreeCmp("25t_350c", type = "Parsimony")

## 25t_1000c
bay_25t_1000c <- read.TreeCmp("25t_1000c", type = "Bayesian")
par_25t_1000c <- read.TreeCmp("25t_1000c", type = "Parsimony")

## 75t_100c
bay_75t_100c <- read.TreeCmp("75t_100c", type = "Bayesian")
par_75t_100c <- read.TreeCmp("75t_100c", type = "Parsimony")

## 75t_350c
bay_75t_350c <- read.TreeCmp("75t_350c", type = "Bayesian")
par_75t_350c <- read.TreeCmp("75t_350c", type = "Parsimony")

## 75t_1000c 
bay_75t_1000c <- read.TreeCmp("75t_1000c", type = "Bayesian")
par_75t_1000c <- read.TreeCmp("75t_1000c", type = "Parsimony")

## 150t_100c
bay_150t_100c <- read.TreeCmp("150t_100c", type = "Bayesian")
par_150t_100c <- read.TreeCmp("150t_100c", type = "Parsimony")

## 150t_350c
bay_150t_350c <- read.TreeCmp("150t_350c", type = "Bayesian")
par_150t_350c <- read.TreeCmp("150t_350c", type = "Parsimony")

## 150t_1000c 
bay_150t_1000c <- read.TreeCmp("150t_1000c", type = "Bayesian")
par_150t_1000c <- read.TreeCmp("150t_1000c", type = "Parsimony")

```

Analysis the differences
===============

Normalise the score
-----------------------------------

Normalising the scores using NTS

```{r, message = FALSE}
## 25t_100c
bay_25t_100c <- NTS(bay_25t_100c, 25)
par_25t_100c <- NTS(par_25t_100c, 25)

## 25t_350c
bay_25t_350c <- NTS(bay_25t_350c, 25)
par_25t_350c <- NTS(par_25t_350c, 25)

## 25t_1000c
bay_25t_1000c <- NTS(bay_25t_1000c, 25)
par_25t_1000c <- NTS(par_25t_1000c, 25)

## Combining into a list
t25_list <- list(
    "c100" = list("bayesian" = bay_25t_100c,
                  "parsimony" = par_25t_100c
                  ),
    "c350" = list("bayesian" = bay_25t_350c,
                  "parsimony" = par_25t_350c
                  ),
    "c1000" = list("bayesian" = bay_25t_1000c,
                   "parsimony" = par_25t_1000c
                   )
                )

## 75t_100c
bay_75t_100c <- NTS(bay_75t_100c, 25)
par_75t_100c <- NTS(par_75t_100c, 25)

## 75t_350c
bay_75t_350c <- NTS(bay_75t_350c, 25)
par_75t_350c <- NTS(par_75t_350c, 25)

## 75t_1000c
bay_75t_1000c <- NTS(bay_75t_1000c, 25)
par_75t_1000c <- NTS(par_75t_1000c, 25)

## Combining into a list
t75_list <- list(
    "c100" = list("bayesian" = bay_75t_100c,
                  "parsimony" = par_75t_100c
                  ),
    "c350" = list("bayesian" = bay_75t_350c,
                  "parsimony" = par_75t_350c
                  ),
    "c1000" = list("bayesian" = bay_75t_1000c,
                   "parsimony" = par_75t_1000c
                   )
                )

## 150t_100c
bay_150t_100c <- NTS(bay_150t_100c, 25)
par_150t_100c <- NTS(par_150t_100c, 25)

## 150t_350c
bay_150t_350c <- NTS(bay_150t_350c, 25)
par_150t_350c <- NTS(par_150t_350c, 25)

## 150t_1000c
bay_150t_1000c <- NTS(bay_150t_1000c, 25)
par_150t_1000c <- NTS(par_150t_1000c, 25)

## Combining into a list
t150_list <- list(
    "c100" = list("bayesian" = bay_150t_100c,
                  "parsimony" = par_150t_100c
                  ),
    "c350" = list("bayesian" = bay_150t_350c,
                  "parsimony" = par_150t_350c
                  ),
    "c1000" = list("bayesian" = bay_150t_1000c,
                   "parsimony" = par_150t_1000c
                   )
                )

```

>>>>

Loading the functions and the data
-----------------------------------

Getting the functions and the data

```{r, eval = TRUE, message = FALSE}
source("functions.R") ; load.functions(test = FALSE)
dyn.load("../Functions/char.diff.so")
load("../Data/NTS/matrix.nts.Rda")
source("../Data/load.data.R")
```

Results
-----------------------------------
